---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body{
background-color: #d3efef;
}
```

## Public Fashion Trends: Footwear, Branding, and Colors

There are three different question about the people's dressing habits. They are "how many of shoes a person have?", "how many of your cloth has visible brand?" and "what color is your most of the cloth?". After collect over 20 people's data, I start to analyse the relationship between those different data. And I have create two summary values down blow which shows the maximum and minimum of amount of shoes a person have and two two bar charts.

```{r} 
# Load the tidyverse package
library(tidyverse)

#read data from the published csv file url into a data frame
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR-bgrw4uy2apdBxggNvSYPYtviMUNOq7tI9ga5MOL79W_2eIyeiUC6VQ4i8FcTHW1mwYEo-sZAJPQ-/pub?output=csv")

# rename the variable and creating a new data frame named latest_data
latest_data <- logged_data %>%
  rename(time = 1,
         shoes_count = 2,
         brand_persentage = 3,
         color = 4)

# using the max() function to find the maximum shoes count for a person in the data
paste("The maximum number of pairs of shoes a person has in the data is",
      max(latest_data$shoes_count),
      ".",
      collapse = " ")

# using the min() function to find the minimum shoes count for a person in the data
paste("The minimum number of pairs of shoes a person has in the data is",
      min(latest_data$shoes_count),
      ".",
      collapse = " ")

# Bar chart 1
latest_data %>%
  ggplot() + 
    geom_bar(aes(x = shoes_count, fill = brand_persentage)) + 
  labs(title = "More shoes, More brand cloths?",
       subtitle = "Comparing the the shoes amount of a person with their brand cloths amount",
       caption = "Source: Student survey",
       x = "Number of shoes for each person",
       y = "The amount of brand cloths the person has")

# Bar chart 2
latest_data %>%
  ggplot() + 
  geom_bar(aes(x = brand_persentage, fill = color)) + 
  labs(title = "Does the color having any relationship between amount of brand cloths for a person?",
       subtitle = "Comparing the the brand_persentage of a person with their cloth prefer color",
       caption = "Source: Student survey",
       x = "The persentage of the amount of brand cloth for each person",
       y = "The color of most of their cloth")

paste("The first summary value is maximum shoes count for a person and the second summary value is minimum shoes count for a person.")
paste("The first bar chart is to see the relationship between the shoes amount of a person and their brand cloths amount the second bar chart is to see the relationship between the color of their cloth and the amount of brand cloths.")

```
